### 2020-06-14 abstract.tex
modified introduction

\begin{abstract}
\label{abstract}
We use smartphones everywhere and concerns have arisen about ``€˜shoulder surfing'',™ or the act of strangers peeking at our phone in public areas. This privacy threat have been studied heavily and various countermeasures have been designed, but mainly against attackers with the naked eye. With the development of smartphones and super resolution (SR) technology, however, we believe that this threat have been underestimated, as a malicious observer can attack from farther away with the assist of his smartphone camera and SR algorithms. We underline this concern by presenting SRPeek, an end-to-end system of shoulder surfing, containing a unique multi-image SR neural network architecture designed for this task, which in this application outperforms other known SR algorithms and fills the blank space of multi-image SR. We prove that our attack is efficient, allowing a human to read 95\% of the text off a smartphone screen at 1.5m range (in the experiment's circumstances) and is robust in different environments. Our SR network can also be used in word recognition tasks with less than ideal images as a preprocessor.
\end{abstract}

>>>>

\begin{abstract}
\label{abstract}
We use smartphones everywhere and concerns have arisen about ``shoulder surfing'', or the act of strangers peeking at our phone in public areas. This privacy threat have been studied heavily and various countermeasures have been designed, but mainly against attackers with the naked eye. With the development of smartphones and super resolution (SR) technology, however, we believe that this threat have been underestimated, as a malicious observer can attack from farther away with the assist of his smartphone camera and SR algorithms. We underline this concern by presenting SRPeek, an end-to-end system of shoulder surfing, containing a unique multi-image SR neural network architecture designed for this task, which in this application outperforms other known SR algorithms and fills the blank space of multi-image SR. We prove that our attack is efficient, allowing a human to read 95\% of the text off a smartphone screen at 1.5m range (in the experiment's circumstances) and is robust in different environments. Our SR network can also be used in word recognition tasks with less than ideal images as a preprocessor.
\end{abstract}

### 2020-06-14 introduction.tex
modified introduction

% introduce LPL asynchronous duty cycle media access
As already we are aware, smartphones have become a necessity in our lives, as we are checking our mobile phones constantly throughout the day. As a result, some concerns of privacy have arisen about nearby parties peeking at our screen, or ‘shoulder surfing’. Although great effort has been put forward to mitigate this threat, from physical privacy films to alternative password entry interfaces \cite{wiedenbeck2006design} \cite{papadopoulos2017illusionpin} and input methods \cite{kumar2007reducing}, these methods often require additional cost and/or effort \cite{Chun2019Keep} and are not widely implemented yet.

On the other hand, many works in this area are built on a threat model of an attacker observing with his/hers naked eye, as they assume that the attacker is not malicious and merely take several peeks out of curiosity. However, it is the rare but malicious and prepared attacker that can do the most harm, and leave aside special equipment, if we only equip the observer with a smartphone, he/she can not only acquire sensitive information from long distances, reducing suspicion, but also record the information for propagating, dealing greater damage to the victim. For example, in a Senate hearing, the Justice Secretary of Philippines, Vitaliano Aguirre II, suffered a leakage of his text messages, as someone had taken a snapshot of his smartphone \cite{Polotiko2017leakage}. Moreover, smartphone cameras have seen great improvement these years, and as a highly-accessible ‘extension of the eye’, it is possible that ‘shoulder surfers’ peek at others’ screen through their smartphone lenses to obtain critical information like passwords or private e-mails. What’s more, recent developments in the field of super resolution (SR) pose a greater threat to smartphone privacy. Attackers can take multiple snapshots of the victim’s screen and process them with multiple image super resolution algorithms in real time, making them able to see clearly while keeping a longer distance. However, most SR methods are designed for and trained on naturally taken images \cite{nasrollahi2020deep} \cite{lyn2020image}; few works have focused on reconstructing blurry snapshots taken at extreme distances, and a new architecture needs to be designed.

To explore this rarely studied privacy threat of the attacker looking through a smartphone camera, we have developed a holistic system for shoulder surfing. The fictional attacker captures multiple images of the victim’s screen in burst mode from his smartphone, and enhances its resolution with our multi-frame super resolution neural network. The network is designed and trained for this purpose, targeting several blurry images taken in quick succession of a screen at a distance. As the information of interest is mostly displayed on screen in the form of text (e.g. passwords or e-mails), our network focuses on reconstructing text, specifically, Chinese characters, English letters, and numbers. The system is deployed on a smartphone for demonstration, capturing and processing images at real time. Our system can also be used as a preprocessor for text-recognition applications when multiple images are available, such as real-time translation apps on a smartphone or text-recognition of video clips.

>>>>

% introduce LPL asynchronous duty cycle media access
As already we are aware, smartphones have become a necessity in our lives, as we are checking our mobile phones constantly throughout the day. As a result, some concerns of privacy have arisen about nearby parties peeking at our screen, or ‘shoulder surfing’. Although great effort has been put forward to mitigate this threat, from physical privacy films to alternative password entry interfaces \cite{wiedenbeck2006design} \cite{papadopoulos2017illusionpin} and input methods \cite{kumar2007reducing}, these methods often require additional cost and/or effort \cite{Chun2019Keep} and are not widely implemented yet on the privacy critical stages (e.g. password entry) of most everyday apps.

On the other hand, many works in this area are built on a threat model of an attacker observing with his/hers naked eye, as they assume that the attacker is not malicious and merely take several peeks out of curiosity. Although studies have shown that a great portion of these attacks are casual and opportunistic without technical equipment\cite{eiband2017understanding}, however, a mere stranger can hardly do any harm reading a fragment of your correspondence or acquiring your password without knowing your account(which, in critical apps like Alipay, seldom appears on screen in common usage). It is the rare but malicious attacker, with certain familiarity and knowledge of the victim, that can do the most harm. The attacker can even be our closest friends or family members, as there are various cases in China where a child obtains Alipay password of their parents, and, unaware that electronic payments consists of 'real' money, ends up spending them lavishly in their games. What's more, specially made equipment are not a necessity for these attacks to happen. If we only equip the observer with a smartphone, he/she can not only acquire sensitive information from long distances, reducing suspicion, but also record the information for propagating, dealing greater damage to the victim. For example, in a Senate hearing, the Justice Secretary of Philippines, Vitaliano Aguirre II, suffered a leakage of his text messages, as someone had taken a snapshot of his smartphone \cite{Polotiko2017leakage}. Moreover, smartphones have seen great improvement these years. Equipped with multiple cameras, the newest generation of smartphones can perform 100x zooming compared to the standard 5x of single camera phones. Improvements in memory hardware also allows burst mode at tremendous frame rates and even high-speed photography, recording videos with thousands of frames per second, and more images means more information. By capturing multiple images of the victim's phone, and processing them with multi-frame super resolution (SR) methods, the attacker can gain vital data from even further away. In this present era where the leakage of a password can cost thousands, and the disclosure of correspondence of public figures can cause huge sensations in media and great damage to the victim, we believe that it's imminent to recall attention on this privacy threat and propose a new standard of screen protection based on modern circumstances.

While exploring this privacy threat, we need to implement a multi-frame SR algorithm on a smartphone in order to monitor the target phone in real time. However, we discovered that there is no published SR algorithm suitable for this scenario. Apparently, the blurriness of the images calls for deep-learning based methods, however most of these methods function on a handful of clearer images(scenary, scanned images, etc.) \cite{nasrollahi2020deep} \cite{lyn2020image}, but we have to merge the information from large quantities of extremely blurred photos, as smartphones can capture 100 snapshots in a few seconds in burst mode, and these photos are taken from extreme distances(to test the theorectical limits of the privacy threat). The different nature between videos and multiple snapshots also rules out the video super resolution methods. The algorithms cannot be adapted to function on larger numbers of input images, because 1) either increased input leads to increases in model complexity, making it unsuitable for mobile deployment, or 2) they lack emphesis on the process of horizontal comparison, relying heavily on the information extracted from each single image, and thus merges the information inefficiency and show unsatisfactory performance.

To explore this privacy threat and to fill the gap in deep-learning based multi-frame super resolution, we designed an end-to-end CNN-based architecture for shoulder surfing and similar multi-frame SR applications with massive input and blurry images. To utilize the large amount of data with low computational complexity, we designed a unique merging layer and placed it between convolutional layers in the SR pipeline. The input images are processed independently and the information extracted are then merged together, serving as a reference for the following convolutions. With the network as core, We then implemented a holistic system for shoulder surfing on a smartphone, which captures multiple images in burst mode, process them with our neural network to generate a high-res image, and repeating this process for constant monitoring. As the information of interest is mostly in the form of text (e.g. passwords or e-mails), our network is trained and evaluated on the task of reconstructing text, specifically, Chinese characters, English letters, and numbers, but we believe that this network architecture can function in all scenarios. Our system can also be used as a preprocessor for text-recognition applications when multiple images are available, such as real-time translation apps on a smartphone or text-recognition on self-driving cars.
